---
title: "Ressources"
format: pdf
---

# R documentation

## Additive survival models

**Flexible Regression Models for Survival Data:** 
<https://cran.r-project.org/web/packages/timereg/refman/timereg.html>

## Super Learner in survival analysis

The super learner requires 3 components:  

1. A library of estimators  
2. A loss function  
3. A model for combining the estimators in the library  

These three components should be tailored to the specific problem. The library 
should be built such that each estimator in the library could individually 
estimate the parameter of interest. The loss function should be chosen to 
reflect the goals of the problem. If one is interested in estimating the hazard, 
the loss function should ideally involve the hazard; if interest in the survival 
function, the loss function should involve the survival function. This may seem 
common sense, but we often see researchers use a hazard loss function when the 
interest is on the survival probability at a specific time point. The loss 
function should be chosen with respect to the problem you are trying to solve. 
The model for combining the estimators in the library is often chosen to 
maintain a bounded loss function for the super learner.

#### Super Learner for survival data by minimizing 
**cross-validated negative partial log-likelihood**

<https://github.com/kgolmakani/SuperLearner-Survival>

Golmakani’s approach builds a Super Learner for survival data by minimizing 
**cross-validated negative partial log-likelihood**. So, the base learners are 
hazard-based learners optimized on Cox partial likelihood. This approach 
optimizes the best convex combination for **hazard ranking**. 

### Survival Super Learner 

*Predicting survival by a Super Learner* (`survivalSL`) 

| Name              | Description |
|-------------------|-------------|
| LIB_COXall        | Proportional hazards (PH) model with all covariates (#) |
| LIB_COXaic        | PH model with covariate selection by AIC minimization (#) |
| LIB_COXen         | PH model with B-spline for quantitative covariates and Elastic-Net penalization (#; hyperparameters: alpha, lambda) |
| LIB_COXlasso      | PH model with B-spline for quantitative covariates and Lasso penalization (#; hyperparameter: lambda) |
| LIB_COXridge      | PH model with B-spline for quantitative covariates and Ridge penalization (#; hyperparameter: lambda) |
| LIB_AFTgamma      | Accelerated failure time (AFT) model with Gamma distribution |
| LIB_AFTggamma     | AFT model with generalized Gamma distribution |
| LIB_AFTllogis     | AFT model with log-logistic distribution |
| LIB_AFTweibull    | AFT model with Weibull distribution |
| LIB_PHexponential | Parametric PH model with Exponential distribution |
| LIB_PHgompertz    | Parametric PH model with Gompertz distribution |
| LIB_PHspline      | PH model with natural cubic spline baseline (hyperparameter: k) |
| LIB_RSF           | Random survival forest (hyperparameters: nodesize, mtry, ntree) |
| LIB_PLANN         | One-layer survival neural network (hyperparameters: n.nodes, decay, batch.size, epochs) |

*Super Learning for conditional survival functions with right-censored data* (`survSuperLearner`)

```{r}
# devtools::install_github("tedwestling/survSuperLearner")
library(survSuperLearner)
survSuperLearner::survlistWrappers()
```

| Wrapper            | Description |
|--------------------|------------|
| survSL.coxph       | Cox proportional hazards model |
| survSL.expreg      | Parametric exponential survival regression |
| survSL.gam         | Generalized additive survival model |
| survSL.km          | Kaplan–Meier estimator |
| survSL.loglogreg   | Log-logistic survival regression |
| survSL.pchreg      | Piecewise constant hazards regression |
| survSL.pchSL       | SuperLearner with piecewise constant hazards |
| survSL.rfsrc       | Random survival forest (randomForestSRC) |
| survSL.template    | Template for custom survival wrapper |
| survSL.weibreg     | Weibull survival regression |

| Wrapper              | Description |
|----------------------|------------|
| All                  | No screening (all variables retained) |
| survscreen.glmnet    | Screening via glmnet penalized regression |
| survscreen.marg      | Marginal screening (univariate survival association) |
| survscreen.template  | Template for custom survival screening |


### Global survival stacking 

```{r}
library(survML)
library(SuperLearner)
SuperLearner::listWrappers()
```

| Wrapper              | Type |
|----------------------|------|
| SL.bartMachine       | Bayesian Additive Regression Trees (BART) |
| SL.bayesglm          | Bayesian generalized linear model |
| SL.biglasso          | Lasso / Elastic-Net (biglasso) |
| SL.caret             | caret unified interface |
| SL.caret.rpart       | caret interface for rpart |
| SL.cforest           | Conditional inference forest |
| SL.earth             | Multivariate Adaptive Regression Splines (MARS) |
| SL.gam               | Generalized additive model |
| SL.gbm               | Gradient boosting machine |
| SL.glm               | Generalized linear model |
| SL.glm.interaction   | GLM with interaction terms |
| SL.glmnet            | Elastic-Net regularized GLM |
| SL.ipredbagg         | Bagged trees (ipred) |
| SL.kernelKnn         | Kernel k-nearest neighbors |
| SL.knn               | k-nearest neighbors |
| SL.ksvm              | Kernel support vector machine |
| SL.lda               | Linear discriminant analysis |
| SL.leekasso          | Leekasso variable selection |
| SL.lm                | Linear model |
| SL.loess             | Local regression (LOESS) |
| SL.logreg            | Logistic regression |
| SL.mean              | Mean predictor |
| SL.nnet              | Neural network |
| SL.nnls              | Non-negative least squares |
| SL.polymars          | Polynomial MARS |
| SL.qda               | Quadratic discriminant analysis |
| SL.randomForest      | Random forest |
| SL.ranger            | Fast random forest (ranger) |
| SL.ridge             | Ridge regression |
| SL.rpart             | CART decision tree |
| SL.rpartPrune        | Pruned CART tree |
| SL.speedglm          | Fast GLM |
| SL.speedlm           | Fast linear model |
| SL.step              | Stepwise selection |
| SL.step.forward      | Forward stepwise selection |
| SL.step.interaction  | Stepwise with interactions |
| SL.stepAIC           | Stepwise AIC selection |
| SL.svm               | Support vector machine |
| SL.template          | Template for custom wrapper |
| SL.xgboost           | Extreme gradient boosting |

| Wrapper               | Type |
|-----------------------|------|
| All                   | No screening (all variables retained) |
| screen.corP           | Correlation screening (p-value based) |
| screen.corRank        | Correlation rank screening |
| screen.glmnet         | Screening via glmnet |
| screen.randomForest   | Screening via random forest importance |
| screen.SIS            | Sure Independence Screening |
| screen.template       | Template for custom screening |
| write.screen.template | Utility to create screening template |

## Permutation variable importance

<https://cran.r-project.org/web/packages/survex/refman/survex.html>

## Random survival forests 

**Random survival forests** 

```{r}
# library(randomForestSRC)
```

**Ensemble methods for survival function estimation with time-varying covariates** (`LTRCforests`) 

```{r}
# devtools::install_github("weichiyao/LTRCforests")
# library(LTRCforests)
```
