---
title: "Model-agnostic variable importance for survival outcomes: a simulation study under additive and mixed hazards"
subtitle: "Simulation protocol"
format: pdf
---

```{r}
library(tidyverse)
library(knitr)
```

# Introduction

We conducted a simulation study to examine the behavior of Wolock’s 
model-agnostic exclusion variable importance measure (VIM) under a range of 
survival data-generating mechanisms. The objectives were to evaluate its 
performance and inferential validity under additive hazards, mixed 
additive–multiplicative hazards, and proportional hazards settings, including 
high-dimensional scenarios with rare binary covariates and heterogeneous effect 
sizes. We also compared alternative strategies for nuisance function estimation 
and contrasted exclusion-based importance with permutation-based importance 
across all scenarios.

# Objectives

The simulation study was designed to evaluate the performance, robustness, and 
inferential validity of Wolock’s model-agnostic exclusion variable importance 
measure (VIM) across several survival data-generating mechanisms.

First, under an **additive hazards framework**, we assess the accuracy and 
inferential properties of the VIM and compare different strategies for 
estimating the conditional survival functions, namely 
***global survival stacking***, ***survival Super Learner***, the 
***Aalen additive hazards model***, and ***random survival forests***.

Second, under **mixed additive and multiplicative hazard structures**, we 
investigate the behavior of the VIM when both types of effects coexist. In this 
setting, conditional survival functions are estimated using 
***global survival stacking***, ***survival Super Learner***, the 
***Cox–Aalen model***, and ***random survival forests***.

Third, we assess the sensitivity of the VIM when covariates correspond to 
**rare alterations** with **heterogeneous effect sizes**, ranging from weak to 
strong, under a **proportional hazards model**.

Finally, we compare **exclusion-based variable importance** with 
**permutation-based variable importance** to examine differences in 
interpretation, stability, and empirical performance across the considered 
scenarios.

# Data-generation mechanisms

## Simulation of covariates 

We simulated datasets combining binary and continuous covariates for 
$i = 1, \dots, n$ individuals.

### Binary covariates

Binary covariates were generated as correlated Bernoulli variables:

$$
X_{ij} \in \{0,1\}, \quad j = 1,\dots,p_B,
$$

where $X_{ij}=1$ indicates the presence of binary feature $j$.

Each variable had marginal prevalence

$$
\pi_j = \Pr(X_{ij}=1).
$$

To induce correlation between variables, a latent Gaussian copula model was used:

$$
\mathbf{Z}_i \sim \mathcal{N}(0,\Sigma_B),
$$

where $\Sigma_B$ is a block-structured correlation matrix.

Binary variables were obtained through probit thresholding:

$$
X_{ij} =
\mathbb{I}\left(
Z_{ij} < \Phi^{-1}(\pi_j)
\right),
$$

where $\Phi^{-1}$ denotes the quantile function of the standard normal distribution. This construction guarantees

$$
\Pr(X_{ij}=1)=\pi_j.
$$

Thus, marginal prevalences are exactly controlled while inducing dependence between binary variables through the latent correlation matrix.

### Continuous covariates

Continuous covariates were simulated from a multivariate normal distribution:

$$
\mathbf{W}_i \sim \mathcal{N}(0,\Sigma_C),
$$

where $\Sigma_C \in \mathbb{R}^{p_C \times p_C}$ is a block-correlation matrix.

Variables were partitioned into $K$ blocks of equal size $b$. For block $k$, define

$$
B_k = \{(k-1)b+1,\dots,kb\}.
$$

The correlation matrix $\Sigma_C=(\sigma_{jl})$ was defined as

$$
\sigma_{jl} =
\begin{cases}
1 & \text{if } j=l, \\
\rho_k & \text{if } j \neq l \text{ and } j,l \in B_k, \\
\rho_B & \text{if } j \in B_k,\; l \in B_m,\; k \neq m.
\end{cases}
$$

Equivalently, each diagonal block can be written as

$$
\Sigma_{C,k}
=
(1-\rho_k)I_b+\rho_k \mathbf{1}_b\mathbf{1}_b^\top,
$$

where $I_b$ denotes the $b \times b$ identity matrix and $\mathbf{1}_b$ is a vector of ones of length $b$.

Continuous covariates were therefore correlated according to a block dependence structure.

## Simulation of time-to-event outcomes

Let $T$ denote the event time and $C$ an independent censoring time. The 
observed data consisted of $(Y,\Delta, X, Z)$, where:

$$Y=min(T,C), \quad \Delta = \mathbb{I}(T \le C).$$
Censoring times were generated independently from an exponential distribution 
to achieve a target censoring proportion.

**Additive Aalen model**

Time-to-event outcomes were generated under an additive hazards framework.  
For each individual $i = 1, \dots, n$, with covariate vector 
$\mathbf{X}_i$, the hazard function was defined as

$$
\lambda(t \mid X_i) = \lambda_0(t) + X_i^\top \alpha,
$$

where $\lambda_0(t)$ denotes the baseline hazard function and 
$\alpha$ represents the vector of additive hazard effects.

**Cox-Aalen model**

To evaluate performance under mixed hazard structures, we additionally 
generated data from a Cox-Aalen model:

$$
\lambda(t|X_i,Z_i)=\lambda_0 \exp(Z_{i}^\top\beta)+X_{i} ^\top\alpha.
$$

where:

* $Z_{i}$ are covariates with multiplicative effects, 
* $\beta$ are multiplicative coefficients,
* $X_{i}$ are covariates with additive effects, 
* $\alpha$ are additive coefficients 

# Target estimands and oracle variable importance 

We considered two estimators of variable importance, targeting distinct 
estimands: exclusion importance and permutation importance.  

## Model-agnostic framework for exclusion-based variable importance in survival analysis 

**Definition**

We consider the model-agnostic variable importance measure proposed by Wolock 
*et al.*, defined through covariate exclusion. For a given prediction time $t_0$ 
and covariate $X_j$, the VIM quantifies the change in predictive performance 
when $X_j$ is removed from the prediction function. 

We defined a nonparametric variable importance measure (VIM) based on the 
predictive value of a pathway set within a flexible survival prediction model 
fitted with `survML`. Let $V(.)$ denote a time-dependent predictive performance 
functional, evaluated on predictions. The variable importance measure for 
covariate $X_j$ at time $t_0$, $\psi_j(t_0)$, was defined as the difference in 
predictive performance between a model fit using the full feature set, 
$V_{full}$ and a model fit after excluding the pathway or group of pathways of 
interest, $V_{reduced}$:
$$\psi_j(P_0) = V_{full} - V_{reduced}$$

**Estimation of the conditional survival functions**

We estimated the conditional survival functions $F_0$ and $G_0$ using different 
strategies, depending on the scenario: 

* Aalen model (`timereg::aalen()`, `pec::predictSurvProb()`)
* Cox-Aalen survival model (`timereg::cox.aalen()`, `pec::predictSurvProb()`) 
* Random survival forests (`randomForestSRC::rfsrc()`) 
* Survival Super Learner (`survivalSL`) 
* Global survival stacking (`survML::stackG()`)

**Estimation of the oracle prediction functions**

We estimated the full and residual oracle prediction functions for time-horizon 
VIMs, $f_{0}$ and $f_{0,s}$, using Super Learner regression.

We used the sample splitting procedure to compute VIM point and standard error 
estimates, from which we computed nominal 95% CI Wald-type confidence intervals. 

## Permutation variable importance in machine learning survival models 

**Definition**

Permutation VIM measures was calculated using `survex` package using the 
`model_parts()` function. The importance of $j$-th variable is defined as the 
change in the loss function $\mathcal{L}$ caused by permutation of this variable 
in the dataset:

$$
\mathrm{PFI}_t(f, \mathbf{X}, j, \mathcal{L}, y)= \frac{1}{B} \sum_{i=1}^{B}
\left( \mathcal{L}(f, \mathbf{X}, y)- 
\mathcal{L}(f, \mathbf{X}^{*j}_i, y) \right)
$$

where $\mathcal{L}$ represents the loss function chosen to evaluate model 
performance, $\mathbf{X}^{*j}_i$ denotes the $i$-th permutation of variable $j$ 
within the dataset $X$, and $B$ is the number of different permutations. 
Permuting a variable is supposed to simulate the loss of information associated 
with the variable.
For `survex`, we used  the `model_parts()` function with 10 permutations.

**Model framework**

We used the following models to calculates variable importance in the loss 
function after the variable values permutations: 

* Aalen model (`timereg`, `pec`) 
* Cox-Aalen survival model (`timereg`, `pec`)
* Random survival forests (`randomForestSRC`) 

## Time horizon 

Variable importance was evaluated at a fixed time horizon, corresponding to **75th percentiles** of the empirical observed event times (or 
the Kaplan-Meier estimator to account for censoring). These represent a late-risk horizon Restricting the analysis to this quantile-based time point reduces computational burden while ensuring that evaluation occurs in regions with a sufficient number of individuals at risk, 
thereby avoiding instability in the tail of the distribution.

## Performance metrics for variable importance in survival analysis 

Variable importance was evaluated using the *Brier score*, $BS(t)$ to captures both discrimination and calibration. We additionally used the 
*cumulative/dynamic area under the ROC curve,* $AUC(t)$ to estimate variable importance measures, which evaluate discrimination independently of calibration. 

The ***cumulative/dynamique AUC*** at time $t$ is defined as the probabilitu 
that, among a randomly selected pair consisting of one individual who experiences 
the event before $t$ and one who survives beyon $t$, the predicted risk is 
higher for the former. 

The ***Brier score*** at time $t$ is the expected squared difference between the 
observed survival status at time $t$ and the predicted survival probability, 
with inverse probability of censoring weights to account for right censoring. 

## Cross-validation procedure 

To ensure fair comparison across nuisance estimation strategies, all models were evaluated using the same cross-validation framework.

Five-fold cross-validation was employed for out-of-sample performance assessment and to prevent optimistic bias in risk prediction and downstream VIM estimation.

We implemented $K$-fold cross-validation with $K=5$. The data were randomly 
partitioned into five approximately equal folds. For each fold:

1. The model was trained on the $K-1$ remaining folds.
2. Predictions of the conditional survival and hazard functions were obtained 
for individuals in the held-out fold.
3. Performance metrics were computed on the validation fold.

This procedure was repeated so that each observation contributed once to 
validation risk estimation.

## Oracle variable importance  

We generated a large Monte Carlo sample ($n=200 000$) from the true 
data-generating model to approximate population-level quantities. Using this sample, we computed the oracle predictive performance as well as the oracle 
VIM measure for each pathway or group of pathways.

# Performance evaluation

The following metrics were computed across $B=1000$ Monte Carlo replications.

| Metric | Definition | Formula |
|--------|------------|----------|
| **Bias** | Average deviation between the estimator and the true parameter | $\frac{1}{B} \sum_{b=1}^{B} (\hat{\theta}^{(b)} - \theta)$ |
| **RMSE** | Root mean squared error measuring overall estimation accuracy | $\sqrt{ \frac{1}{B} \sum_{b=1}^{B} (\hat{\theta}^{(b)} - \theta)^2 }$ |
| **Coverage** | Proportion of confidence intervals containing the true parameter | $\frac{1}{B} \sum_{b=1}^{B} \mathbf{1}(\theta \in CI^{(b)})$ |
| **CI width** | Average length of confidence intervals | $\frac{1}{B} \sum_{b=1}^{B} (U^{(b)} - L^{(b)})$ |
| **Type I Error** | Probability of rejecting $H_0$ when it is true | $\frac{1}{B} \sum_{b=1}^{B} \mathbf{1}(p^{(b)} < \alpha)$ under $H_0$ |
| **Power** | Probability of rejecting $H_0$ when the alternative is true | $\frac{1}{B} \sum_{b=1}^{B} \mathbf{1}(p^{(b)} < \alpha)$ under $H_1$ |
| **Rank correlation** | Correlation between true and estimated parameter rankings |  |
| **Runtime** | Average computational time per replication | $\frac{1}{B} \sum_{b=1}^{B} t^{(b)}$ |

where:

- $B$ is the number of Monte Carlo replications,
- $\theta$ is the true parameter,
- $\hat{\theta}^{(b)}$ is the estimate in replication $b$,
- $CI^{(b)} = [L^{(b)}, U^{(b)}]$,
- $\alpha$ is the nominal significance level.

# Simulation scenarios 

The main scenarios are summarized in @tbl-scen. 

```{r}
#| label: "tbl-scen"
#| tbl-cap: "Summary of the main scenarios"

tbl_scen <- tibble(
  scenario_id = 1:2,
  hazards = c("Additive hazards (Aalen model)",
              "Mixed additive and multiplicative hazards (Cox-Aalen model)"),
  # p = c(4, 6),
  var_sim = c("$X_1 \\sim Bernoulli(0.4)$ <br> $X_2$ <br> $X_3$ <br> $X_4$",
              "$X_1$ <br> $X_2$ <br> $X_3$ <br> $Z_1$ <br> $Z_2$ <br> $Z_3$"),
  coef = c(paste("$\\alpha_{1}=0.1$ <br> $\\alpha_{2}=0.05$ <br>",
                 "$\\alpha_{3}=0.005$ <br> $\\alpha_{4}=0$"),
           paste("$\\alpha_{1}=0.1$ <br> $\\alpha_{2}=0.05$ <br> $\\alpha_{3}=0$",
                 "<br> $\\beta_{1}=1$ <br> $\\beta_{2}=0.5$ <br> $\\beta_{3}=0$")),
  nuisance = c("Aalen model <br> Survival Super Learner <br> Global survival stacking",
               "Cox-Aalen model <br> Survival Super Learner <br> Global survival stacking")
  
)
kable(tbl_scen, col.names = c("Scenario n°", "Effect type",# "$p$",
                              "Simulation of covariates", "Coefficient", 
                              "Nuisance function estimation"))
```

## Scenario 1 - Additive hazards (baseline benchmark) 

**Objective**

This baseline scenario evaluates the robustness of Wolock's model-agnostic
variable importance measure (VIM) under correct model specification.
Specifically, we assess whether competing nuisance-function estimators
recover the true exclusion VIM when the data-generating mechanism follows
an **additive hazards model**.

**Data generating mechanism**

Four binary covariates were generated *independently* with prevalences spanning 
rare to frequent alterations, $X_j \sim Bernoulli(0.4)$. 

Events times were simulated under the following time-constant additive hazards 
model: 

$$\lambda(t|x)=\lambda_0(t)+\alpha_{1}(t)X_{1}+\alpha_{2}(t)X_{2}+\alpha_{3}(t)X_{3}+\alpha_{4}(t)X_{4}$$

with $\lambda_0(t)=0.05$ (constant) and $\alpha_j(t)=(0.1, 0.05, 0.005, 0)$. 

Independent censoring times were generated as $C \sim Uniform(0, c_{max})$. The
parameter $c_{max}$ was calibrated using a large Monte Carlo sample from the 
data-generating mechanism to achieve an expected censoring proportion of 
approximately 20%, and the calibrated value was then fixed across all 
simulation replicates. 

**Nuisance functions estimators to compare**

We compare the following approaches for estimating the nuisance functions 
required for VIM computation:

* Aalen additive hazards model (`timereg::aalen`)
* Survival Super Learner (`survivalSL`)
* Global survival stacking (`survML`)

Since the data-generating mechanism follows an additive hazards model,
the additive Aalen estimator is correctly specified. The remaining
methods introduce varying degrees of model misspecification,
allowing us to assess the robustness of the VIM procedure
to nuisance-model choice.

## Scenario 2 - Mixed additive and multiplicative effects 

**Objective**

This scenario evaluate the sensitivity of the exclusion VIM when the true 
hazard follows a **Cox-Aalen model**.

**Data-generating mechanism**

The covariates are generated *independently* as follows:

* $X = (X_{1}, X_{2}, X_{3}, Z_{1}, Z_{2}, Z_{3})$
* $X_{1}, X_{2}, X_{3} \sim \mathcal{B}(0.4)$
* $Z_{1}, Z_{2} \sim \mathcal{B}(0.4)$
* $Z_{3} \sim \mathcal{N}(0,1)$

To generate mixed additive and multiplicative effects, event times were 
simulated under a Cox-Aalen model with constant baseline hazard: 
$\lambda_0(t)=0.05$. Additive effects were assigned to $X_1$, $X_2$ and $X_3$ 
with coefficients $\alpha_{1}(t)=0.1$, $\alpha_{2}=0.05$ and $\alpha_{3}(t)=0$, 
respectively. Multiplicative (proportional hazards) effects were assigned to 
$X_1$, $X_2$ and $X_3$ with coefficients $\beta_{1}=1$, $\beta_{2}=0.5$ and
$\beta_{3}=0$. 

Independent censoring times were generated as $C \sim Uniform(0, c_{max})$. The
parameter $c_{max}$ was calibrated using a large Monte Carlo sample from the 
data-generating mechanism to achieve an expected censoring proportion of 
approximately 20%, and the calibrated value was then fixed across all 
simulation replicates. 

**Nuisance functions estimators to compare**

We compare the following approaches for estimating the nuisance functions 
required for VIM computation:

* Cox-Aalen model (`timereg::cox.aalen`)
* Survival Super Learner (`survivalSL`)
* Global survival stacking (`survML`)

## Scenario 3 -  Rare alterations with 

**Objective**

This scenario aims to evaluate the overall performance of the VIM procedure to ***rare alterations*** exhibiting ***heterogeneous effect sizes (ranging from weak to strong)*** under a ***proportional hazards model***. More specifically, the objective is to assess whether the VIM approach can:

* detect rare yet highly prognostic alterations,
* discriminate between strong and moderate prognostic signals, and
* correctly identify non-informative (null) variables.

**Data-generating mechanisms**

All covariates were generated independently as binary variables: 

$$X_j \sim \mathcal{B}(\pi_j)$$ with $\pi \in {\{0.01, 0.1\}}$ to reflect genomic rarity. 

The event times follows a Aalen or Cox-Aalen model (cf. scenario 1 and 2).

Covariates were partitioned according to both their prevalence and prognostic effect size, resulting in the following combinations:

```{r}
knitr::kable(
  data.frame(
    prev_category = c(
      rep("Very rare", 3),
      rep("Rare", 3)
    ),
    prev = c(
      rep("$\\pi = 0.01$", 3),
      rep("$\\pi = 0.10$", 3)),
    effect = rep(c("Strong", "Moderate", "Null"), 2),
    alpha = rep(c(0.1, 0.05, 0), 2),
    beta = rep(c(1, 0.5, 0), 2)
  ),
  escape = FALSE,
  align = "llcc",
  col.names = c("Prevalence category","$\\pi_j$","Effect category","$\\alpha$","$\\beta$")
)
```

This design allows us to assess whether the VIM procedure can detect rare but strongly prognostic alterations, distinguish strong from moderate effects, and correctly assign low importance to null variables.

Independent censoring times were generated as $C \sim Uniform(0, c_{max})$. The parameter $c_{max}$ was calibrated using a large Monte Carlo sample from the data-generating mechanism to achieve an expected censoring proportion of approximately 20%, and the calibrated value was then fixed across all 
simulation replicates. 

## Sensitivity to covariate correlations 

For each scenario, we additionally evaluated the sensitivity of the VIM to 
correlations between covariates. Correlations were introduced between selected 
covariates while preserving their marginal distributions (binary or continuous). 
Specifically, we considered both weak and moderate correlation dependence 
between predictors, with pairwise correlations set to $\rho=0.3$ and $\rho=0.6$, 
respectively. This analysis allows us to assess the robustness of the estimated 
VIM in the presence of correlated covariates. 

## Compare exclusion variable importance to permutation variable importance

**Objective**

To examine differences in interpretation, stability, and empirical performance 
across the considered scenarios.

**Scenarios**

- Additive hazards 
- Mixed additive and multiplicative hazards 

## True values of variable importance for all scenarios 

The approximate true values of variable importance based on Brier score, and 
AUC(t) under all scenarios considered here are provided in Table X 
(to be completed). 

# R documentation

## Additive survival models

**Flexible Regression Models for Survival Data:** 
<https://cran.r-project.org/web/packages/timereg/refman/timereg.html>

## Super Learner in survival analysis

The super learner requires 3 components:  

1. A library of estimators  
2. A loss function  
3. A model for combining the estimators in the library  

These three components should be tailored to the specific problem. The library 
should be built such that each estimator in the library could individually 
estimate the parameter of interest. The loss function should be chosen to 
reflect the goals of the problem. If one is interested in estimating the hazard, 
the loss function should ideally involve the hazard; if interest in the survival 
function, the loss function should involve the survival function. This may seem 
common sense, but we often see researchers use a hazard loss function when the 
interest is on the survival probability at a specific time point. The loss 
function should be chosen with respect to the problem you are trying to solve. 
The model for combining the estimators in the library is often chosen to 
maintain a bounded loss function for the super learner.

#### Super Learner for survival data by minimizing 
**cross-validated negative partial log-likelihood**

<https://github.com/kgolmakani/SuperLearner-Survival>

Golmakani’s approach builds a Super Learner for survival data by minimizing 
**cross-validated negative partial log-likelihood**. So, the base learners are 
hazard-based learners optimized on Cox partial likelihood. This approach 
optimizes the best convex combination for **hazard ranking**. 

### Survival Super Learner 

*Predicting survival by a Super Learner* (`survivalSL`) 

| Name              | Description |
|-------------------|-------------|
| LIB_COXall        | Proportional hazards (PH) model with all covariates (#) |
| LIB_COXaic        | PH model with covariate selection by AIC minimization (#) |
| LIB_COXen         | PH model with B-spline for quantitative covariates and Elastic-Net penalization (#; hyperparameters: alpha, lambda) |
| LIB_COXlasso      | PH model with B-spline for quantitative covariates and Lasso penalization (#; hyperparameter: lambda) |
| LIB_COXridge      | PH model with B-spline for quantitative covariates and Ridge penalization (#; hyperparameter: lambda) |
| LIB_AFTgamma      | Accelerated failure time (AFT) model with Gamma distribution |
| LIB_AFTggamma     | AFT model with generalized Gamma distribution |
| LIB_AFTllogis     | AFT model with log-logistic distribution |
| LIB_AFTweibull    | AFT model with Weibull distribution |
| LIB_PHexponential | Parametric PH model with Exponential distribution |
| LIB_PHgompertz    | Parametric PH model with Gompertz distribution |
| LIB_PHspline      | PH model with natural cubic spline baseline (hyperparameter: k) |
| LIB_RSF           | Random survival forest (hyperparameters: nodesize, mtry, ntree) |
| LIB_PLANN         | One-layer survival neural network (hyperparameters: n.nodes, decay, batch.size, epochs) |

*Super Learning for conditional survival functions with right-censored data* (`survSuperLearner`)

```{r}
# devtools::install_github("tedwestling/survSuperLearner")
library(survSuperLearner)
survSuperLearner::survlistWrappers()
```

| Wrapper            | Description |
|--------------------|------------|
| survSL.coxph       | Cox proportional hazards model |
| survSL.expreg      | Parametric exponential survival regression |
| survSL.gam         | Generalized additive survival model |
| survSL.km          | Kaplan–Meier estimator |
| survSL.loglogreg   | Log-logistic survival regression |
| survSL.pchreg      | Piecewise constant hazards regression |
| survSL.pchSL       | SuperLearner with piecewise constant hazards |
| survSL.rfsrc       | Random survival forest (randomForestSRC) |
| survSL.template    | Template for custom survival wrapper |
| survSL.weibreg     | Weibull survival regression |

| Wrapper              | Description |
|----------------------|------------|
| All                  | No screening (all variables retained) |
| survscreen.glmnet    | Screening via glmnet penalized regression |
| survscreen.marg      | Marginal screening (univariate survival association) |
| survscreen.template  | Template for custom survival screening |


### Global survival stacking 

```{r}
library(survML)
library(SuperLearner)
SuperLearner::listWrappers()
```

| Wrapper              | Type |
|----------------------|------|
| SL.bartMachine       | Bayesian Additive Regression Trees (BART) |
| SL.bayesglm          | Bayesian generalized linear model |
| SL.biglasso          | Lasso / Elastic-Net (biglasso) |
| SL.caret             | caret unified interface |
| SL.caret.rpart       | caret interface for rpart |
| SL.cforest           | Conditional inference forest |
| SL.earth             | Multivariate Adaptive Regression Splines (MARS) |
| SL.gam               | Generalized additive model |
| SL.gbm               | Gradient boosting machine |
| SL.glm               | Generalized linear model |
| SL.glm.interaction   | GLM with interaction terms |
| SL.glmnet            | Elastic-Net regularized GLM |
| SL.ipredbagg         | Bagged trees (ipred) |
| SL.kernelKnn         | Kernel k-nearest neighbors |
| SL.knn               | k-nearest neighbors |
| SL.ksvm              | Kernel support vector machine |
| SL.lda               | Linear discriminant analysis |
| SL.leekasso          | Leekasso variable selection |
| SL.lm                | Linear model |
| SL.loess             | Local regression (LOESS) |
| SL.logreg            | Logistic regression |
| SL.mean              | Mean predictor |
| SL.nnet              | Neural network |
| SL.nnls              | Non-negative least squares |
| SL.polymars          | Polynomial MARS |
| SL.qda               | Quadratic discriminant analysis |
| SL.randomForest      | Random forest |
| SL.ranger            | Fast random forest (ranger) |
| SL.ridge             | Ridge regression |
| SL.rpart             | CART decision tree |
| SL.rpartPrune        | Pruned CART tree |
| SL.speedglm          | Fast GLM |
| SL.speedlm           | Fast linear model |
| SL.step              | Stepwise selection |
| SL.step.forward      | Forward stepwise selection |
| SL.step.interaction  | Stepwise with interactions |
| SL.stepAIC           | Stepwise AIC selection |
| SL.svm               | Support vector machine |
| SL.template          | Template for custom wrapper |
| SL.xgboost           | Extreme gradient boosting |

| Wrapper               | Type |
|-----------------------|------|
| All                   | No screening (all variables retained) |
| screen.corP           | Correlation screening (p-value based) |
| screen.corRank        | Correlation rank screening |
| screen.glmnet         | Screening via glmnet |
| screen.randomForest   | Screening via random forest importance |
| screen.SIS            | Sure Independence Screening |
| screen.template       | Template for custom screening |
| write.screen.template | Utility to create screening template |

## Permutation variable importance

<https://cran.r-project.org/web/packages/survex/refman/survex.html>

## Random survival forests 

**Random survival forests** 

```{r}
library(randomForestSRC)
```

**Ensemble methods for survival function estimation with time-varying covariates** (`LTRCforests`) 

```{r}
# devtools::install_github("weichiyao/LTRCforests")
library(LTRCforests)
```

# References 
