---
title: "Model-agnostic variable importance for survival outcomes: a simulation study under additive and mixed hazards"
subtitle: "Simulation protocol"
author: "Stacy Cyrille"
date: last-modified
format: 
  pdf:
    include-in-header:
      text: |
        \usepackage{pdflscape}
number-sections: true
link-citations: true
---

```{r}
library(tidyverse)
library(knitr)
```

# Introduction

We conducted a simulation study to examine the behavior of Wolock’s 
model-agnostic exclusion variable importance measure (VIM) under a range of 
survival data-generating mechanisms. The objectives were to evaluate its 
performance and inferential validity under additive hazards, mixed 
additive–multiplicative hazards, and proportional hazards settings, including 
high-dimensional scenarios with rare binary covariates and heterogeneous effect 
sizes. We also compared alternative strategies for nuisance function estimation 
and contrasted exclusion-based importance with permutation-based importance 
across all scenarios.

# Objectives

The simulation study was designed to evaluate the performance, robustness, and 
inferential validity of Wolock’s model-agnostic exclusion variable importance 
measure (VIM) across several survival data-generating mechanisms.

First, under an **additive hazards framework**, we assess the accuracy and 
inferential properties of the VIM and compare different strategies for 
estimating the conditional survival functions, namely 
***global survival stacking***, ***survival Super Learner***, the 
***Aalen additive hazards model***, and ***random survival forests***.

Second, under **mixed additive and multiplicative hazard structures**, we 
investigate the behavior of the VIM when both types of effects coexist. In this 
setting, conditional survival functions are estimated using 
***global survival stacking***, ***survival Super Learner***, the 
***Cox–Aalen model***, and ***random survival forests***.

Third, we assess the sensitivity of the VIM when covariates correspond to 
**rare alterations** with **heterogeneous effect sizes**, ranging from weak to 
strong, under a **proportional hazards model**.

<!-- Finally, we compare **exclusion-based variable importance** with  -->
<!-- **permutation-based variable importance** to examine differences in  -->
<!-- interpretation, stability, and empirical performance across the considered  -->
<!-- scenarios. -->

# Data-generation mechanisms

## Simulation of covariates 

We simulated datasets combining binary and continuous covariates for 
$i = 1, \dots, n$ individuals.

### Binary covariates

Binary covariates were generated as correlated Bernoulli variables:

$$
X_{ij} \in \{0,1\}, \quad j = 1,\dots,p_B,
$$

where $X_{ij}=1$ indicates the presence of binary feature $j$.

Each variable had marginal prevalence

$$
\pi_j = \Pr(X_{ij}=1).
$$

To induce correlation between variables, a latent Gaussian copula model was used:

$$
\mathbf{Z}_i \sim \mathcal{N}(0,\Sigma_B),
$$

where $\Sigma_B$ is a block-structured correlation matrix.

Binary variables were obtained through probit thresholding:

$$
X_{ij} =
\mathbb{I}\left(
Z_{ij} < \Phi^{-1}(\pi_j)
\right),
$$

where $\Phi^{-1}$ denotes the quantile function of the standard normal distribution. This construction guarantees

$$
\Pr(X_{ij}=1)=\pi_j.
$$

Thus, marginal prevalences are exactly controlled while inducing dependence between binary variables through the latent correlation matrix.

### Continuous covariates

Continuous covariates were simulated from a multivariate normal distribution:

$$
\mathbf{W}_i \sim \mathcal{N}(0,\Sigma_C),
$$

where $\Sigma_C \in \mathbb{R}^{p_C \times p_C}$ is a block-correlation matrix.

Variables were partitioned into $K$ blocks of equal size $b$. For block $k$, define

$$
B_k = \{(k-1)b+1,\dots,kb\}.
$$

The correlation matrix $\Sigma_C=(\sigma_{jl})$ was defined as

$$
\sigma_{jl} =
\begin{cases}
1 & \text{if } j=l, \\
\rho_k & \text{if } j \neq l \text{ and } j,l \in B_k, \\
\rho_B & \text{if } j \in B_k,\; l \in B_m,\; k \neq m.
\end{cases}
$$

Equivalently, each diagonal block can be written as

$$
\Sigma_{C,k}
=
(1-\rho_k)I_b+\rho_k \mathbf{1}_b\mathbf{1}_b^\top,
$$

where $I_b$ denotes the $b \times b$ identity matrix and $\mathbf{1}_b$ is a vector of ones of length $b$.

Continuous covariates were therefore correlated according to a block dependence structure.

## Simulation of time-to-event outcomes

Let $T$ denote the event time and $C$ an independent censoring time. The 
observed data consisted of $(Y,\Delta, X, Z)$, where:

$$Y=min(T,C), \quad \Delta = \mathbb{I}(T \le C).$$
Censoring times were generated independently from an exponential distribution 
to achieve a target censoring proportion.

**Additive Aalen model**

Time-to-event outcomes were generated under an additive hazards framework.  
For each individual $i = 1, \dots, n$, with covariate vector 
$\mathbf{X}_i$, the hazard function was defined as

$$
\lambda(t \mid X_i) = \lambda_0(t) + X_i^\top \alpha,
$$

where $\lambda_0(t)$ denotes the baseline hazard function and 
$\alpha$ represents the vector of additive hazard effects.

**Cox-Aalen model**

To evaluate performance under mixed hazard structures, we additionally 
generated data from a Cox-Aalen model:

$$
\lambda(t|X_i,Z_i)=\lambda_0 \exp(Z_{i}^\top\beta)+X_{i} ^\top\alpha.
$$

where:

* $Z_{i}$ are covariates with multiplicative effects, 
* $\beta$ are multiplicative coefficients,
* $X_{i}$ are covariates with additive effects, 
* $\alpha$ are additive coefficients 

# Target estimands and oracle variable importance 

We considered two estimators of variable importance, targeting distinct 
estimands: exclusion importance and permutation importance.  

## Model-agnostic framework 
<!-- for exclusion-based variable importance in survival analysis  -->

**Definition**

We consider the model-agnostic variable importance measure proposed by Wolock 
*et al.*, based on a covariate exclusion principle [@Wolock2024]. For a given prediction 
a predefined time horizon $t_0$ and covariate (or covariate group) $X_s$, the VIM 
quantifies the loss in predictive performance induced by removing $X_s$ from 
the prediction model. Using flexible survival prediction framework, we defined 
the non-parametric VIM measure for $X_s$ as 
$$\psi_{s}(P_0) = V(f_{0}) - V(f_{0,-s})$$

where $V(f_0)$ denotes the prediction model fitted using the complete set of 
covariates, and $V(f_{0,-s})$ the model fitted after excluding $X_s$. 

Thus, $\psi_{s}(P_0)$ measures the incremental predictive contribution of $X_s$
at prediction time $t_0$, with larger values indicating greater importance. 

**Details on nuisance parameter and oracle prediction functions estimation**

We estimated the conditional survival functions $F_0$ and $G_0$ using several
modeling strategies depending on the simulation setting: 

The conditional event and censoring survival functions, denoted respectively 
by $F_0$ and $G_0$, were estimated using the learning strategies summarized 
in [@tbl-survival-learners](#tbl-survival-learners).

```{r}
#| label: tbl-survival-learners
#| tbl-cap: "Learning strategies used to estimate nuisance parameters."
#| tbl-colwidths: [30, 40, 30]

knitr::kable(
  data.frame(
    Method = c(
      "Aalen model",
      "Cox-Aalen model",
      "Survival Super Learner",
      "Global survival stacking"#,
      # "Random survival forests"
    ),
    Implementation = c(
      "`timereg::aalen()` \\ `pec::predictSurvProb()`",
      "`timereg::cox.aalen()` \\ `pec::predictSurvProb()`",
      "`survivalSL::survivalSL` \\ `survivalSL::predict.sltime()`",
      "`survML::stackG()`"#,
      # "`randomForestSRC::rfsrc()`"
    ),
    Reference = c(
      "[@Therneau2007]",
      "[@Therneau2007]",
      "[@survivalsl]",
      "[@Wolock2024pp]"#,
      # ""
    )
  ),
  escape = FALSE,
  align = c("l", "l", "l"),
  col.names = c("Method", "R implementation", "Reference")
)
```

<!-- * Aalen model (`timereg::aalen()`, `pec::predictSurvProb()`) -->
<!-- * Cox-Aalen survival model (`timereg::cox.aalen()`, `pec::predictSurvProb()`)  -->
<!-- * Survival Super Learner (`survivalSL`) [@survivalsl] -->
<!-- * Global survival stacking (`survML::stackG()`) [@Wolock2024pp] -->
<!-- * Random survival forests (`randomForestSRC::rfsrc()`)  -->

For time-horizon VIMs, the full oracle prediction function $f_0$ is a simple 
transformation of $F_0$ and was not estimated separately in the experiments. 
We estimated the residual oracle prediction function, $f_{0,s}$, using Super 
Learner regression [@Laan2007].

[@tbl-survML-param](#tbl-survML-param) gives the algorithms included in the Super Learner 
library for global survival stacking and estimation of the residual oracle 
prediction function $f_{0,s}$ for VIM estimation. Five-fold cross-validation 
was used to determine the optimal convex combination of these learners that 
minimized cross-validated squared-error loss, as described
in @Wolock2024. 

```{r}
#| label: "tbl-survML-param"
#| tbl-cap: "Algorithms used in the Super Learner for global survival stacking and for estimation of the residual oracle prediction function for VIM estimation."
#| tbl-colwidths: [30, 40, 30]

tbl_survML <- tibble(
  algo_name = c("`SL.mean`",
                "`SL.gam`",
                "`SL.ranger`",
                "`SL.xgboost`"),
  algo_desc = c("Marginal mean",
                "Generalized additive model",
                "Random forest",
                "Gradient-boosted trees"),
  tune = c("NA",
           "NA",
           "default",
           paste("`ntrees` $\\in \\{250, 500, 1000\\}$",
                 "`max_depth` $\\in \\{1,2\\}$",
                 sep = " \\ "))
  
)
tbl_survML %>%
  kable(escape = FALSE,
        col.names = c("Algorithme name", 
                      "Algorithm description",
                      "Tuning parameters"))
```

[@tbl-survivalSL-param](#tbl-survivalSL-param) gives the algorithms 
included in the survival Super Learner library [@survivalsl]. 

```{r}
#| label: "tbl-survivalSL-param"
#| tbl-cap: "Algorithms used in the survival Super Learner."

tibble(
  algo_name = c("`LIB_COXall`", 
                "`LIB_PHexponential`", 
                "`LIB_RSF`"),
  algo_desc = c("Usual Cox model",
                "Exponential-distributed PH model",
                "Survival random forest"),
  tune = rep("Default",3)
  
)%>%
  kable(escape = FALSE,
        col.names = c("Algorithme name", 
                      "Algorithm description",
                      "Tuning parameters"))
```

For global survival stacking, estimates for distributions were produced 
simultaneously. The Aalen and Cox-Aalen models, as well as the random survival 
forest algorithm were fitted twice, once to estimate $F_0$ and once to 
estimate $G_0$. 

We used the sample splitting procedure to compute VIM point and standard error 
estimates, from which we computed nominal 95% CI Wald-type confidence intervals. 

<!-- ## Permutation variable importance in machine learning survival models  -->

<!-- **Definition** -->

<!-- Permutation VIM measures was calculated using `survex` package using the  -->
<!-- `model_parts()` function [@Spytek2023]. The importance of $j$-th variable is defined as the  -->
<!-- change in the loss function $\mathcal{L}$ caused by permutation of this variable  -->
<!-- in the dataset: -->

<!-- $$ -->
<!-- \mathrm{PFI}_t(f, \mathbf{X}, j, \mathcal{L}, y)= \frac{1}{B} \sum_{i=1}^{B} -->
<!-- \left( \mathcal{L}(f, \mathbf{X}, y)-  -->
<!-- \mathcal{L}(f, \mathbf{X}^{*j}_i, y) \right) -->
<!-- $$ -->

<!-- where $\mathcal{L}$ represents the loss function chosen to evaluate model  -->
<!-- performance, $\mathbf{X}^{*j}_i$ denotes the $i$-th permutation of variable $j$  -->
<!-- within the dataset $X$, and $B$ is the number of different permutations.  -->
<!-- Permuting a variable is supposed to simulate the loss of information associated  -->
<!-- with the variable. -->
<!-- For `survex`, we used  the `model_parts()` function with 10 permutations. -->

<!-- **Model framework** -->

<!-- We used the following models to calculates variable importance in the loss  -->
<!-- function after the variable values permutations:  -->

<!-- * Aalen model (`timereg`, `pec`)  -->
<!-- * Cox-Aalen survival model (`timereg`, `pec`) -->
<!-- * Random survival forests (`randomForestSRC`)  -->

## Time horizon 

Variable importance was evaluated at a fixed time horizon, corresponding to 
**75th percentiles** of the empirical observed event times (or 
the Kaplan-Meier estimator to account for censoring). These represent a 
late-risk horizon. Restricting the analysis to this quantile-based time point 
reduces computational burden while ensuring that evaluation occurs in regions 
with a sufficient number of individuals at risk, 
thereby avoiding instability in the tail of the distribution.

## Performance metrics 

Variable importance was evaluated using the *Brier score*, $BS(t)$ to captures 
both discrimination and calibration. We additionally used the 
*cumulative/dynamic area under the ROC curve,* $AUC(t)$ to estimate variable 
importance measures, which evaluate discrimination independently of calibration. 

The ***Brier score*** at time $t$ is the expected squared difference between the 
observed survival status at time $t$ and the predicted survival probability, 
with inverse probability of censoring weights to account for right censoring. 

The ***cumulative/dynamique AUC*** at time $t$ is defined as the probabilitu 
that, among a randomly selected pair consisting of one individual who experiences 
the event before $t$ and one who survives beyon $t$, the predicted risk is 
higher for the former. 

## Oracle variable importance  

We generated a large Monte Carlo sample ($n=200 000$) from the true 
data-generating model to approximate population-level quantities. Using this 
sample, we computed the oracle predictive performance as well as the oracle 
VIM measure for each variables.

# Performance evaluation

The performance of the proposed methods was evaluated across $B=1000$ Monte 
Carlo replications using the metrics summarized in 
[@tbl-performance-metrics](#tbl-performance-metrics). These criteria assess 
estimation accuracy, inferential validity, ranking performance, and 
computational efficiency.

```{r}
#| label: tbl-performance-metrics
#| tbl-cap: "Performance metrics used to evaluate estimation accuracy, inference, ranking ability, and computational efficiency across simulation replicates."
#| tbl-colwidths: [20, 40, 40]

knitr::kable(
  data.frame(
    Metric = c(
      "Bias",
      "RMSE",
      "Coverage",
      "CI width",
      "Type I Error",
      "Power",
      "Rank correlation",
      "Runtime"
    ),
    Definition = c(
      "Average deviation between the estimator and the true parameter",
      "Root mean squared error measuring overall estimation accuracy",
      "Proportion of confidence intervals containing the true parameter",
      "Average length of confidence intervals",
      "Probability of rejecting $H_0$ when it is true",
      "Probability of rejecting $H_0$ when the alternative is true",
      "Correlation between true and estimated parameter rankings",
      "Average computational time per replication"
    ),
    Formula = c(
      "$\\frac{1}{B} \\sum_{b=1}^{B} (\\hat{\\theta}^{(b)} - \\theta)$",
      "$\\sqrt{ \\frac{1}{B} \\sum_{b=1}^{B} (\\hat{\\theta}^{(b)} - \\theta)^2 }$",
      "$\\frac{1}{B} \\sum_{b=1}^{B} \\mathbf{1}(\\theta \\in CI^{(b)})$",
      "$\\frac{1}{B} \\sum_{b=1}^{B} (U^{(b)} - L^{(b)})$",
      "$\\frac{1}{B} \\sum_{b=1}^{B} \\mathbf{1}(p^{(b)} < \\alpha)$ under $H_0$",
      "$\\frac{1}{B} \\sum_{b=1}^{B} \\mathbf{1}(p^{(b)} < \\alpha)$ under $H_1$",
      "",
      "$\\frac{1}{B} \\sum_{b=1}^{B} t^{(b)}$"
    )
  ),
  escape = FALSE,
  align = c("l", "l", "c"),
  col.names = c("Metric", "Definition", "Formula")
)
```

$B$ denotes the number of Monte Carlo replications, $\theta$ the true parameter 
value, $\hat{\theta}^{(b)}$ the estimate obtained at replication $b$, 
$CI^{(b)} = [L^{(b)}, U^{(b)}]$ the corresponding confidence interval, 
and $\alpha$ the nominal significance level.

# Simulation scenarios 

The main scenarios of the simulation study are summarized in [@tbl-scen](#tbl-scen). 

<!-- ```{=latex} -->
<!-- \begin{landscape} -->
<!-- ``` -->

```{r}
#| label: "tbl-scen"
#| tbl-cap: "Summary of the main scenarios"
#| tbl-colwidths: [3, 18, 26, 33, 20]

tbl_scen <- tibble(
  scenario_id = c("S1","S2"),
  hazards = c("Additive hazards (Aalen model)",
              "Mixed additive and multiplicative hazards (Cox-Aalen model)"),
  # p = c(4, 6),
  var_sim = c("$X_1, X_2, X_3, X_4 \\sim \\mathcal{B}(0.4)$", 
              paste("$X_1, X_2, X_3 \\sim \\mathcal{B}(0.4)$",
                    "$Z_1, Z_2 \\sim \\mathcal{B}(0.4)$",
                    "$Z_3 \\sim \\mathcal{N}(0,1)$",
                    sep ="$\\newline$")),
  coef = c(paste("$\\alpha_{1}=0.1$ (strong effect)", 
                 "$\\alpha_{2}=0.05$ (moderate effect)",
                 "$\\alpha_{3}=0.005$ (weak effect)",
                 "$\\alpha_{4}=0$ (null effect)",
                 sep = "$\\newline$"),
           paste("$\\alpha_{1}=0.1$ (strong effect)",
                 "$\\alpha_{2}=0.05$ (moderate effect)",
                 "$\\alpha_{3}=0$ (null effect)",
                 "$\\beta_{1}=1$ (strong effect)",
                 "$\\beta_{2}=0.5$ (moderate effect)",
                 "$\\beta_{3}=0$ (null effect)",
                 sep = "$\\newline$")),
  nuisance = c("Aalen model $\\newline$ Survival Super Learner $\\newline$ Global survival stacking",
               "Cox-Aalen model $\\newline$ Survival Super Learner $\\newline$ Global survival stacking")
  
)
kable(tbl_scen, escape = FALSE, 
      col.names = c("  ", "Effect type",# "$p$",
                    "Covariates", 
                    "Coefficient", 
                    "Nuisance parameters estimation"))
```

<!-- ```{=latex} -->
<!-- \end{landscape} -->
<!-- ``` -->

## Scenario 1 (S1) - Additive hazards 

This scenario evaluates the robustness of Wolock's model-agnostic
variable importance measure (VIM) under correct model specification.
Specifically, we assess whether competing nuisance-function estimators
recover the true exclusion VIM when the data-generating mechanism follows
an **additive hazards model**.

Four binary covariates were generated *independently* as follows: 
$X_{1}, X_{2}, X_{3} \sim \mathcal{B}(0.4)$.

Events times were simulated under the following time-constant additive hazards 
model: 

$$\lambda(t|x)=\lambda_0(t)+\alpha_{1}(t)X_{1}+\alpha_{2}(t)X_{2}+\alpha_{3}(t)X_{3}+\alpha_{4}(t)X_{4}$$

with $\lambda_0(t)=0.05$ (constant) and $\alpha_j(t)=(0.1, 0.05, 0.005, 0)$. 

Independent censoring times were generated as $C \sim Uniform(0, c_{max})$. The
parameter $c_{max}$ was calibrated using a large Monte Carlo sample from the 
data-generating mechanism to achieve an expected censoring proportion of 
approximately 20%, and the calibrated value was then fixed across all 
simulation replicates. 

We compared several approaches for estimating the nuisance functions required 
for VIM computation, including the Aalen additive hazards model, the survival 
Super Learner, and global survival stacking.

The approximate true values of variable importance based on $AUC(t)$ and, Brier 
score ($BS(t)$) under this scenario are provided in 
[@tbl-true-vim-s1](#tbl-true-vim-s1).

```{r}
#| label: "tbl-true-vim-s1"
#| tbl-cap: "Approximate true values of variable importance for S1"

vars_aalen <- c("$X_1$", "$X_2$", "$X_3$", "$X_4$")
vars_cox_aalen <- c("$\\psi_{X_1}$", "$\\psi_{X_2}$", "$\\psi_{X_3}$",
                    "$\\psi_{Z_1}$", "$\\psi_{Z_2}$", "$\\psi_{Z_3}$")

tibble(
  vars = unlist(lapply(vars_aalen, 
                       function(x) c(x, rep("", 2)))),
  method = rep(c("Aalen",
                 "survival Super Learner",
                 "Global survival stacking"),
               length(vars_aalen)),
  auc_vim = rep(c("","",""), each = length(vars_aalen)),
  brier_vim = rep(c("","",""), each = length(vars_aalen))
)%>%
  kable(
    col.names = c("Variable",
                  "Nuisance parameter estimation", 
                  "AUC($t_{0.75}$) VIM",
                  "BS($t_{0.75}$) VIM"),
    align = rep("l", 4),
    escape = FALSE
  )
```

## Scenario 2 (S2) - Mixed additive and multiplicative effects 

This scenario evaluate the sensitivity of the exclusion VIM when the true 
hazard follows a **Cox-Aalen model**.

The covariates are generated *independently* as follows:

* $X_{1}, X_{2}, X_{3}, Z_{1}, Z_{2} \sim \mathcal{B}(0.4)$
* $Z_{3} \sim \mathcal{N}(0,1)$

To generate mixed additive and multiplicative effects, event times were 
simulated under a Cox-Aalen model with constant baseline hazard: 
$\lambda_0(t)=0.05$. Additive effects were assigned to $X_1$, $X_2$ and $X_3$ 
with coefficients $\alpha_{1}(t)=0.1$, $\alpha_{2}=0.05$ and $\alpha_{3}(t)=0$, 
respectively. Multiplicative (proportional hazards) effects were assigned to 
$Z_1$, $Z_2$ and $Z_3$ with coefficients $\beta_{1}=1$, $\beta_{2}=0.5$ and
$\beta_{3}=0$. 

Independent censoring times were generated as $C \sim Uniform(0, c_{max})$. The
parameter $c_{max}$ was calibrated using a large Monte Carlo sample from the 
data-generating mechanism to achieve an expected censoring proportion of 
approximately 20%, and the calibrated value was then fixed across all 
simulation replicates. 

We compared several approaches for estimating the nuisance functions required 
for VIM computation, including the Cox-Aalen model, the survival 
Super Learner, and global survival stacking.

The approximate true values of variable importance based on $AUC(t)$ and, Brier 
score ($BS(t)$) under this scenario are provided in 
[@tbl-true-vim-s2](#tbl-true-vim-s2).

```{r}
#| label: "tbl-true-vim-s2"
#| tbl-cap: "Approximate true values of variable importance for S2"

vars_cox_aalen <- c("$X_1$", "$X_2$", "$X_3$",
                    "$Z_1$", "$Z_2$", "$Z_3$")

tibble(
  vars = unlist(lapply(vars_cox_aalen, 
                       function(x) c(x, rep("", 2)))),
  method = rep(c("Cox-Aalen",
                 "survival Super Learner",
                 "Global survival stacking"),
               length(vars_cox_aalen)),
  auc_vim = rep(c("","",""), each = length(vars_cox_aalen)),
  brier_vim = rep(c("","",""), each = length(vars_cox_aalen))
)%>%
  kable(
    col.names = c("Variable",
                  "Nuisance parameter estimation", 
                  "AUC($t_{0.75}$) VIM",
                  "BS($t_{0.75}$) VIM"),
    align = rep("l", 4),
    escape = FALSE
  )
```

## Additional numerical experiments 

### Sensitivity to low-prevalence covariates 

This scenario evaluates the overall performance of the VIM procedure 
to ***low-prevalence covariates*** with ***heterogeneous prognostic effects***,
ranging from null to strong, under both additive and mixed 
additive-multiplicative hazard structures. The objective is to assess 
whether the model-agnostic VIM approach can identify rare yet highly prognostic 
covariates, discriminate between moderate and strong effects, and correctly 
detect non-informative variables.

Covariates were generated with different marginal prevalences and effect sizes, 
leading to the simulation settings summarized in 
[@tbl-sims-prev](#tbl-sims-prev). These experiments were designed to assess 
the sensitivity of the proposed approach to low-prevalence covariates and 
varying levels of prognostic signal.

```{r}
#| label: "tbl-sims-prev"
#| tbl-cap: "Simulation settings assessing sensitivity to low-prevalence covariates"

knitr::kable(
  data.frame(
    prev_category = c(
      rep("Very rare", 3),
      rep("Rare", 3)
    ),
    prev = c(
      rep("$\\pi = 0.01$", 3),
      rep("$\\pi = 0.10$", 3)),
    effect = rep(c("Strong", "Moderate", "Null"), 2),
    alpha = rep(c(0.1, 0.05, 0), 2),
    beta = rep(c(1, 0.5, 0), 2)
  ),
  escape = FALSE,
  align = "llcc",
  col.names = c("Prevalence category","$\\pi_j$","Effect category","$\\alpha$","$\\beta$")
)
```

### Sensitivity to covariate correlations 

For each scenario, we additionally evaluated the sensitivity of the VIM to 
correlations between covariates. Correlations were introduced between selected 
covariates while preserving their marginal distributions (binary or continuous). 
Specifically, we considered both weak and moderate correlation dependence 
between predictors, with pairwise correlations set to $\rho=0.3$ and $\rho=0.6$, 
respectively. This analysis allows us to assess the robustness of the estimated 
VIM in the presence of correlated covariates. 

<!-- ### Compare exclusion variable importance to permutation variable importance -->

<!-- **Objective** -->

<!-- To examine differences in interpretation, stability, and empirical performance  -->
<!-- across the considered scenarios. -->

<!-- **Scenarios** -->

<!-- - Additive hazards  -->
<!-- - Mixed additive and multiplicative hazards  -->

# References 
